cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-12 paper-cardinalR.Rmd
Added all arguments

```{r}
arg_branching_tb <- tibble(arg = c("n", "k", "p", "h", "ratio", "s", "r", "k_small", "r_vec", "spe", "w", "steps", "spins", "hc", "non_fac"), 
                          type = c("integer", "integer", "integer", "real value",
                                   "real value", "real value", "real value", "integer", "real values", "real value", "real value", "integer", "integer", "real value", "real value"),
                        exp = c("Number of points.",
                                "Number of clusters.",
                                "Number of dimensions.",
                                "Height.",
                                "Radius tip to radius base ratio.",
                                "Variance-covariance matrix.",
                                "Radius.",
                                "Number of small spheres.",
                                "Radius of the big and small spheres.",
                                "How far the small spheres are placed from each other.",
                                "Vertical variation",
                                "Number of steps for the theta parameter.",
                                "Number of loops of the spiral.",
                                "Steepness and vertical scaling of the hyperbola.",
                                "Strength of this sinusoidal effect.")) |> 
   mutate(arg = gsub("_", "\\\\_", arg))
```

>>>>

```{r}
arg_branching_tb <- tibble(arg = c("n", "k", "p", "h", "ratio", "s", "r", "n_vec", "k_small", "r_vec", "spe", "w", "steps", "spins", "hc", "non_fac"), 
                          type = c("integer", "integer", "integer", "real value",
                                   "real value", "real value", "real value", "integers", "integer", "real values", "real value", "real value", "integer", "integer", "real value", "real value"),
                        exp = c("Number of points.",
                                "Number of clusters.",
                                "Number of dimensions.",
                                "Height.",
                                "Radius tip to radius base ratio.",
                                "Variance-covariance matrix.",
                                "Radius.",
                                "Sample sizes of the big and small spheres",
                                "Number of small spheres.",
                                "Radius of the big and small spheres.",
                                "How far the small spheres are placed from each other.",
                                "Vertical variation",
                                "Number of steps for the theta parameter.",
                                "Number of loops of the spiral.",
                                "Steepness and vertical scaling of the hyperbola.",
                                "Strength of this sinusoidal effect.")) |> 
   mutate(arg = gsub("_", "\\\\_", arg))
```
